User-level Grid Monitoring with Inca 2

### 2007-02-27 papers/hpdc-gmw-2007/paper.tex
my mods to grasp section -- cathie can you do a quick pass on this for accuracy to make sure I didn't change the content in a bad way
git-svn-id: file:///localdisk/subversion/inca/trunk/pubs@6576 7dba3f4a-8be6-0310-8b3b-b4fec25ea7f3

% Describe GrASP probes
The Grid Assessment Probes (GrASP)~\cite{grasp} are designed to 
serve as simple grid application kernel exemplars as well as a 
set of diagnostic tools. They test and measure performance of 
basic grid functions including file transfers, remote execution, 
and Grid Information Services response.  There are two basic probes: i.  The
circle probe takes a 100 MB file and passes it in a ring through a given set
of grid nodes, measuring transfer time at each step.  ii.  The gather probe
transfers a 100 MB file from some number of source nodes to a compute node,
runs a computation through the job queue on the compute resource and then
transfers a 100 MB file to a single destination node.  The transfer of the
first set of files is executed in parallel.  Once again all tranfers times, as
well as compute and queue times are recorded.

The GrASP probes yield useful data on the performance and reliability of the
grid infrastructure that they are run on.  In order for the data gathered to
be useful, it must gathered repeatedly over time and stored in a manner
appropriate for querying.  In addition to storing the measurements available
we also required that any error messages encountered be stored as well.    
In order to
fulfill the last 2 requirements we deployed the GrASP probes as reporters
within the Inca framework.

The GrASP probes have been written to follow the specifications of an Inca
reporter.  Porting the original code to follow the specifications proved to be
trivial.  Inca was also used to store all of the GrASP data and related error
messages.

\begin{figure}[tbp]
  \centering
  \mbox{\epsfig{file=errorHistogramTG.eps, width=\columnwidth}}
  \caption{\label{errorHist_fig} Histogram of Error Messages Encountered.}
\end{figure}

\subsubsection{Results}

GrASP, using Inca, was deployed on TeraGrid and Geon for a period of over 6
months.  The data gathered during that period yielded a paper, Measuring the
Performance and Reliability of Production Computational Grids ~\cite{grasp2}.
By the running of the GrASP probes over such an extended period of time
we were able to identify a recurring Globus 2 bug.  Figure ~\ref{errorHist_fig} shows the types (shortened) and number of system errors that were detected while executing the
benchmark during the GrASP deployment on TeraGrid in 2005. The highest occurring
error was number 9, Assertion GLOBUS FALSE, which was the result of a bug in
the Globus 2 GRAM server.  We were also able to predict the
execution time of Preco, a Grid application run on the TeraGrid within 12\% (excluding setup and cleanup time).

>>>>

% Describe GrASP probes
The Grid Assessment Probes (GrASP)~\cite{grasp} are designed to 
serve as simple grid application kernel exemplars as well as a 
set of diagnostic tools. They test and measure the performance of 
basic Grid functions including file transfers, remote execution, 
and information services queries.  There are two basic probes: circle and 
gather.  The circle probe transfers a 100 MB file around a ring of
Grid nodes and measures the transfer time at each step.  The gather probe
transfers a 100 MB file from some number of source nodes to a compute node,
runs a computation through the job queue on the compute resource, and then
transfers a 100 MB file to a single destination node.  The transfer of the
first set of files is executed in parallel.  Once again all tranfers times, as
well as compute and queue times are recorded.

The GrASP probes yield useful data on the performance and reliability of the
Grid infrastructure that they are run on.  As such, data must be gathered 
repeatedly over time and archived.
In addition to storing the performance measurements,
any error messages encountered must be stored as well.    
In order to
fulfill the last two requirements, the GrASP probes were modified
to follow the reporter specifications and deployed using Inca.
Porting the original code to follow the reporter specifications proved to be
trivial.  A number of scripts were then written to graph and analyze the GrASP
data and related error messages stored in the Inca depot.

\begin{figure}[tbp]
  \centering
  \mbox{\epsfig{file=errorHistogramTG.eps, width=\columnwidth}}
  \caption{\label{errorHist_fig} Number and types of errors collected by
  GrASP benchmark execution over a six-month period on TeraGrid.}
\end{figure}

Using Inca, GrASP was deployed on TeraGrid and GEON for a period of over 6
months.  The data gathered during that period yielded a paper~\cite{grasp2}.
One result was that a recurring Globus 2 bug was identified as shown in Figure ~\ref{errorHist_fig}.  The figure shows the types (shortened) and number of system errors that were detected while executing 
GrASP on TeraGrid in 2005. The highest occurring
error was number 9, Assertion GLOBUS FALSE, which was the result of a bug in
the Globus 2 GRAM server.  Furthermore, the execution time of Preco, a Grid application run on the TeraGrid, was predicted within 12\% (excluding setup and cleanup time).
